Equivalence Hypergraphs: E-Graphs for Monoidal Theories

### 2023-11-19 sections/combinatorial_semantics.tex
Parent relation for pushout is now proven correct

@@

    \item $\phi(<_{c,\mathcal{F}}^{\mu}(x)) = <_{c,\mathcal{G}}^{\mu}(\phi(x))$.
          \update{We do not require such an equation when $[x) = \varnothing$}.

@@

    First, we assume that $Z$ is a \textit{discrete} e-hypergraph, i.e. it has no edges.

@@

    Recall that $<_{c}$ is essentially a transitive clousure of $<_{c}^{\mu}$ and hence we can first define $<_{c,\sfrac{X+Y}{\sim}}^{\mu}([u]_{E})$ and $<_{c,\sfrac{X+Y}{\sim}}^{\mu}([u]_{V})$.

@@

    Assume that $u$ is an element of $V_{X+Y}$.

@@

              The last condition means that there exists $e_y = <_{c,Y}^{\mu}(g_{V}(z))$.
              We then define $<_{c,\sfrac{X+Y}{\sim}}^{\mu}([u]) = [g_{V};<_{c,Y}^{\mu};i_{2,E}(z)] = [i_{2,E}(e_y)]$.

@@

              The one before the last condition means that there exists $e_x = <_{c,X}^{\mu}(f_{V}(z))$.
              We then define $<_{c,\sfrac{X+Y}{\sim}}^{\mu}([u]) = [f_{V};<_{c,X}^{\mu};i_{1,E}(z)] = [i_{1,E}(e_x)]$.
        \item $u$ has no pre-image in $Z$ and then $<_{c,\sfrac{X+Y}{\sim}}^{\mu}([u]) = [<_{c,X+Y}^{\mu}(u)]$

@@

              Hence, we define $<_{c,\sfrac{X+Y}{\sim}}^{\mu}([u]) = [<_{c,X+Y}^{\mu}(u)]$.

@@

    \question{I decided to keep Z discrete, otherwise the number of cases to consider within the proofs is too large.
    This also means that we now can identify only nodes.
    I will make changes to account for this later.
    }
    \update{If $f$ and $g$ are not mono, the definitions stay the same as $i_{2,E}$ and $i_{1,E}$ are mono.}
    Clearly, all the cases above are disjoint.
    Let's check that this is a well-defined function.
    Suppose $t_1, t_2$ are nodes and $t_1 \sim t_2$, then $<_{c,\sfrac{X+Y}{\sim}}^{\mu}([t_1]) = <_{c,\sfrac{X+Y}{\sim}}^{\mu}([t_2])$.
    $t_1 \sim t_2$ implies there is $z$ such that $t_1 = f_{V};i_{1,V}(z)$ and $t_2 = g_{V};i_{2,V}(z)$ and either $[f_{V}(t_1)) = \varnothing$ or $[g_{V}(z)) = \varnothing$.
    Assume the latter, then, by definition.
        <_{c,\sfrac{X+Y}{\sim}}^{\mu}([t_1]) = [f_{V};<_{c,X}^{\mu};i_{1,E}(z)]    
        <_{c,\sfrac{X+Y}{\sim}}^{\mu}([t_2]) = [f_{V};<_{c,X}^{\mu};i_{1,E}(z)]    
    so we have well-defined-ness on the nose.

@@

    We also need to makes sure that $[]_{E} : E_{X} + E_{Y} \to \sfrac{E_{X} + E_{Y}}{\sim}$ and $[]_{V} : V_{X} + V_{Y} \to \sfrac{V_{X} + V_{Y}}{\sim}$ are homomorphisms.
    \begin{enumerate}
        \item $s_{X+Y};[]_{V}^{*}(e) = []_{E};s_{\sfrac{X+Y}{\sim}}(e)$
              This is the same as in $\catname{Hyp_{\Sigma}}$.
        \item $[<_{c,X+Y}^{\mu}(e)]_{E} = <_{c,\sfrac{X+Y}{\sim}}^{\mu}([e]_{E})$ for $e$ such that $[e) \not = \varnothing$.
              This is homomorphic by definition. 
        \item $[<_{c,X+Y}^{\mu}(v)]_{E} = <_{c,\sfrac{X+Y}{\sim}}^{\mu}([v]_{V})$.
              Let's make case analysis on $[v]_{V}$.
              \begin{itemize}
                \item $v$ has a pre-image $z$ in $V_{Z}$ such that $v = f_{V};i_{1,V}(z)$.
                    \begin{itemize}
                        \item If $[f_{V}(z)) = \varnothing$ and $[g_{V}(z)) \not = \varnothing$, then, because $i_{1,V}$ is a coproduct injection, it must be the case that $[i_{1,V}(f_{V}(z))) = \varnothing$ and we do not require any equalities for such $v$.
                        \item If $[f_{V}(z)) \not = \varnothing$ and $[g_{V}(z)) = \varnothing$, then,
                              by definition, we have $<_{c,\sfrac{X+Y}{\sim}}^{\mu}([v]) = [f_{V};<_{c,X};i_{1,E}(z)] = [i_{1,E}(<_{c,Y}^{\mu}(f_{V}(z)))] = [i_{1,E}(e_y)]$.
                              Because $i_{1,E}$ is a homomorphism, we also have $[<_{c,X+Y}^{\mu}(f_{V};i_{1,V}(z))] = [i_{1,E}(<_{c,Y}^{\mu}(f_{V}(z)))] = [i_{1,E}(e_y)]$.
                    \end{itemize}
                \item The case when $v = g_{V};i_{2,V}(z)$ is symmetric.
                \item If $v$ has no pre-image in $V_{Z}$ then homomorphism-ness of $[]_{V}$ is similar to the case for $[]_{V}$ above.
              \end{itemize}
    \end{enumerate}

@@

    \update{Check that $<_{c,\sfrac{X+Y}{\sim}}^{\mu}$ is irreflexive and assymetric and that it respects connectivity.}
    \begin{itemize}
        \item Suppose there exist $[e]$ such that $[e] = <_{c,\sfrac{X+Y}{\sim}^{\mu}}([e]) = [<_{c,X+Y}^{\mu}(e)]$ and $e = <_{c,X+Y}^{\mu}(e)$ because edges are not identified.
              This is not possible as $<_{c,X+Y}^{\mu}$ is irreflexive. We need not to check this requirement for nodes because a node can not be a predecessor.
        \item Let $e_1,e_2$ be edges. 
              Then, if $[e_1] <_{c,\sfrac{X+Y}{\sim}}^{\mu}([e_2])$ it must not be the case that $[e_2] <_{c,\sfrac{X+Y}{\sim}}^{\mu}([e_1])$.
              We have $[e_1] = [<_{c,X+Y}^{\mu}(e_2)]$ and if it was the case that $[e_2] <_{c,\sfrac{X+Y}{\sim}}([e_1])$ then $[e_2] = <_{c,X+Y}^{\mu}(e_1)$ which would mean that $<_{c,X+Y}$ is not assymetric.
              Once again, we do not need to check for nodes as a node can not be on the lefthand side of the relation.
        \item We need to show that if $[v] \in s([e_1])$ and $[e_2] <_{c,\sfrac{X+Y}{\sim}}^{\mu}([e_1])$ then $[e_2] <_{c,\sfrac{X+Y}{\sim}}^{\mu}([v])$.
              We have $e_2 = <_{c,X+Y}^{\mu}(e_1)$ and $[v] \in [s(e_1)]^{*}$ meaning 
              that there exists $v' \in s(e_1)$ such that $[v] = [v']$.
              \begin{itemize}
                        \item $v' = v$. Then, given $e_2 = <_{c,X+Y}^{\mu}(e_1)$ it must be the case that $e_2 = <_{c,X+Y}^{\mu}(v)$ and $[e_2] = [<_{c,X+Y}^{\mu}(v)] = <_{c,\sfrac{X+Y}{\sim}}^{\mu}([v])$.
                        \item $v' \sim v$ and there exists $z \in V_{Z}$ such that $v = f_{V};i_{1,V}(z)$ and $v' = g_{V};i_{2,V}(z)$ and $v' \in s(e_1)$ and because $e_2 <_{c,X+Y}^{\mu}(e_1)$ it must be the case that $e_2 <_{c,X+Y}^{\mu}(v')$. This also means that necessarily $[g_{V}(z)) \not = \varnothing$ and $[f_{V}(z)) = \varnothing$.
                              If $[f_{V}(z)) = \varnothing$, then $<_{c,\sfrac{X+Y}{\sim}}^{\mu}([v]) = [g_{V};<_{c,Y};i_{2,E}(z)] = [<_{c,Y}^{\mu};i_{2,E}(g_{V}(z))] = [<_{c,X+Y}^{\mu}(i_{2,V}(g_{B}(z)))] = [<_{c,X+Y}^{\mu}(v')] = [e_2]$.
                        \item Case when $v' = f_{V};i_{1,V}(z)$ is symmetric.
               \end{itemize}
            \end{itemize}
    Let's now define $\conflict_{\sfrac{X+Y}{\sim}}$.
    We can consider the original conflict relation as a function $\conflict_{X+Y} : (V_{X} + V_{Y}) + (E_{X} + E_{Y}) \to 2^{(V_{X} + V_{Y}) + (E_{X} + E_{Y})}$.
    Quotienting the range of the function gives us $\conflict_{X+Y}' : V_{X} + V_{Y} + E_{X} + E_{Y} \to 2^{(\sfrac{V_{X} + V_{Y}}{\sim}) + \sfrac{(E_{X} + E_{Y})}{\sim}}$, which is essentially $\langle []_{V};i_{\sfrac{V_{X} + V_{Y}}{\sim}}, []_{E};i_{\sfrac{E_{X} + E_{Y}}{\sim}} \rangle^{*}$ (a copairing extended to sequences that we will further denote it as $\langle []_{V}^{\conflict} []_{E}^{\conflict} \rangle$) applied to the return value of $\conflict_{X+Y}$.
    We then define the new relation as

>>>>

\begin{remark}
    Both relations can be considered as functions defined on $V_{\mathcal{F}} + E_{\mathcal{F}}$, i.e. on the coproduct of nodes and edges.
    To make things well-typed, we will use corresponding coproduct injections $i_{V_{\mathcal{F}}} \to V_{\mathcal{F}} + E_{\mathcal{F}}$ and $i_{E_{\mathcal{F}}} \to V_{\mathcal{F}} + E_{\mathcal{F}}$ when passing either node or edge into these functions.
    For example, an immediate successor of a node $x$ can be written functionally as $<_{c,\mathcal{F}}^{\mu}(i_{V_{\mathcal{F}}}(x))$.
\end{remark}

@@

    \item \[
        \phi_{E}(<_{c,\mathcal{F}}^{\mu}(i_{V_{\mathcal{F}}}(x))) = <_{c,\mathcal{G}}^{\mu}(\phi_{V};i_{V_{\mathcal{G}}}(x))
        \] when $x$ is a node,
        and
        \[
        \phi_{E}(<_{c,\mathcal{F}}^{\mu}(i_{E_{\mathcal{F}}}(x))) = <_{c,\mathcal{G}}^{\mu}(\phi_{E};i_{E_{\mathcal{G}}}(x))  
        \] when $x$ is an edge.
          \update{We do not require such an equation when $[x) = \varnothing$}.

@@

    \begin{itemize}
    \item First, we assume that $Z$ is a \textit{discrete} e-hypergraph, i.e. it has no edges.
    \item Second, we assume that $[f_{V}(v_i)) = [f_{V}(v_j))$ and $[g_{V}(v_i)) = [g_{V}(v_j))$ for all $v_i,v_j \in V_{Z}$. \update{This essentially means that $f,g$ do not map nodes to levels of different hierarchy.}
    \label{pushout:assumptions}
    \end{itemize}

@@

    Recall that $<_{c}$ is essentially a transitive clousure of $<_{c}^{\mu}$ and hence we can first define 
    \[<_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{E_{X} + E_{Y}}{\sim}}[u]_{E})
    \] and 
        <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}[u]_{V})
    \] where $i_*$ are injections into $\sfrac{V_{X} + V_{Y}}{\sim} + \sfrac{E_{X} + E_{Y}}{\sim}$.

@@

    Assume that $u$ is an element of $V_{X+Y}$ and

@@

              The last condition means that there exists $e_y = <_{c,Y}^{\mu}(i_{V_{Y}}(g_{V}(z)))$.
              We then define 
                <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}[u]) = [g_{V};i_{V_{Y}};<_{c,Y}^{\mu};i_{2,E}(z)] = [i_{2,E}(e_y)]

@@

              The one before the last condition means that there exists $e_x = <_{c,X}^{\mu}(i_{V_{X}}(f_{V}(z)))$.
              We then define 
                <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}[u]) = [f_{V};i_{V_{X}};<_{c,X}^{\mu};i_{1,E}(z)] = [i_{1,E}(e_x)]
        \item $u$ has no pre-image in $Z$ and then 
            <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}[u]) = [<_{c,X+Y}^{\mu}(i_{V_{X} + V_{Y}}(u))]

@@

              Consider two cases.
                \item  $<_{c,X+Y}^{\mu}(i_{E_{X} + E_{Y}}(u)) = u_1$.
                        Then we define
                        <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{E_{X} + E_{Y}}{\sim}}[u]) = [<_{c,X+Y}^{\mu}(i_{E_{X} + E_{Y}}(u))]
                \item $[u) = \varnothing$ and for all $v_i \in s(u)$ and $v_j \in t(u)$ $[[v_i]) \not = \varnothing$ and $[[v_j]) \not = \varnothing$.
                      Then we define 
                        <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{E_{X} + E_{Y}}{\sim}}[u]) = <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}[v])
                    \] where $v$ is either in $s([u])$ or $t([u])$.
                     The second assumption in~\ref{pushout:assumptions} guarantees that all candidates for $[v]$ share the same predecessor, i.e. the definition does not depend on a particular $[v]$.

@@

    \begin{remark}
        Essentially, what we build above is that $[e] = <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}([v]))$ when there exists $v' \in V_{X} + V_{Y}$ such that $[v'] = [v]$ and $e = <_{c,X+Y}^{\mu}(v')$.
    \end{remark}
    \update{If $f$ and $g$ are not mono, the definitions stay the same as $i_{2,E}$ and $i_{1,E}$ are mono.}
    Clearly, all the cases above are disjoint.

    Let's check that this is a well-defined function.
    Suppose $t_1, t_2$ are nodes and $t_1 \sim t_2$, then $<_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X}+V_{Y}}{\sim}}[t_1]) = <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}[t_2])$.
    $t_1 \sim t_2$ implies there is $z$ such that $t_1 = f_{V};i_{1,V}(z)$ and $t_2 = g_{V};i_{2,V}(z)$ and two cases
    \begin{itemize}
        \item $[f_{V}(z)) \not = \varnothing$ and $[g_{V}(t_2)) = \varnothing$
        \item $[f_{V}(z)) = \varnothing$ and $[g_{V}(t_2)) \not = \varnothing$
    \end{itemize} 
    Consider the first case, then, by definition.
    \[
        <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}[t_1]) = [f_{V};i_{V_{X}};<_{c,X}^{\mu};i_{1,E}(z)]
    \]
    and
    \[
        <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}[t_2]) = [f_{V};i_{V_{X}};<_{c,X}^{\mu};i_{1,E}(z)]
    \]
    so we have well-defined-ness on the nose. We do not need to check well-defined-ness for edges as $e_1 \sim e_2$ just implies $e_1 = e_2$ for edges.

@@

    We also need to makes sure that $[]_{E} : E_{X} + E_{Y} \to \sfrac{E_{X} + E_{Y}}{\sim}$ and $[]_{V} : V_{X} + V_{Y} \to \sfrac{V_{X} + V_{Y}}{\sim}$ are homomorphisms.
    \begin{enumerate}
        \item $s_{X+Y};[]_{V}^{*}(e) = []_{E};s_{\sfrac{X+Y}{\sim}}(e)$
              This is the same as in $\catname{Hyp_{\Sigma}}$.
        \item $[<_{c,X+Y}^{\mu}(i_{E_{X} + E_{Y}}(e))]_{E} = <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}([e]_{E}))$ for $e$ such that $[e) \not = \varnothing$.
              Note that by requiring $[e) \not = \varnothing$ we use the first definition for edges.
              This is homomorphic by definition. 
        \item $[<_{c,X+Y}^{\mu}(i_{V_{X} + V_{Y}}(v))]_{E} = <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}([v]_{V}))$.
              Let's make case analysis on $[v]_{V}$.
              \begin{itemize}
                \item $v$ has a pre-image $z$ in $V_{Z}$ such that $v = f_{V};i_{1,V}(z)$.
                    \begin{itemize}
                        \item If $[f_{V}(z)) = \varnothing$ and $[g_{V}(z)) \not = \varnothing$, then, because $i_{1,V}$ is a coproduct injection, it must be the case that $[i_{1,V}(f_{V}(z))) = \varnothing$ and we do not require any equalities for such $v$.
                        \item If $[f_{V}(z)) \not = \varnothing$ and $[g_{V}(z)) = \varnothing$, then,
                              by definition, we have $<_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{V_{X} + V_{Y}}[v]) = [f_{V};i_{V_{X}};<_{c,X}^{\mu};i_{1,E}(z)] = [i_{1,E}(<_{c,X}^{\mu}(f_{V};i_{V_{X}}(z)))] = [i_{1,E}(e_x)]$.
                              Because $i_{1,E}$ is a homomorphism, we also have $[<_{c,X+Y}^{\mu}(f_{V};i_{1,V};i_{V_{X} + V_{Y}}(z))] = [i_{1,E}(<_{c,X}^{\mu}(f_{V};i_{V_{X}}(z)))] = [i_{1,E}(e_x)]$.
                    \end{itemize}
                \item The case when $v = g_{V};i_{2,V}(z)$ is symmetric.
                \item If $v$ has no pre-image in $V_{Z}$ then homomorphism-ness of $[]_{V}$ is similar to the case for $[]_{E}$ above.
              \end{itemize}
    \end{enumerate}

@@

    \update{Check that $<_{c,\sfrac{X+Y}{\sim}}^{\mu}$ is irreflexive and assymetric and that it respects connectivity.}
        \item Suppose there exist $[e]$ such that $[e] = <_{c,\sfrac{X+Y}{\sim}^{\mu}}(i_{\sfrac{E_{X} + E_{Y}}{\sim}}([e]))$.
              Then we have two cases.
                \item Assume $<_{c,X+Y}^{\mu}(i_{E_{X} + E_{Y}}(e)) = e_1$, then  $<_{c,\sfrac{X+Y}{\sim}^{\mu}}(i_{\sfrac{E_{X} + E_{Y}}{\sim}}([e])) = [e_1]$. 
                      This would mean that $e_1 = e$ which would mean that the relation $<_{c,X+Y}^{\mu}$ is not irreflexive.
                \item Assume $[e) = \varnothing$ and for all $v_{i} \in s(e)$ and $v_{j} \in t(e)$ $[[v_i]) \not = \varnothing$ $[[v_j]) \not = \varnothing$.
                      Then, $<_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{E_{X} + E_{Y}}{\sim}}([e])) = <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}([v]))$.
                        \item If $v$ has no pre-image in $V_{Z}$, then $<_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}([v])) = [<_{c,X+Y}^{\mu}(i_{V_{X} + V_{Y}}(v))] = [e]$.
                              This would mean that $e$ is a predecessor of $v$ in $X+Y$, but $v$ is either in the sources or targets of $e$ which violates respectful connectivity condition.
                        \item $v$ has a pre-image $f_{V};i_{1,V}(z)$ in $V_{Z}$ such that $[f_{V}(z)) \not = \varnothing$ and $[g_{V}(z)) = \varnothing$.
                              Then, $<_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}([v])) = [i_{1,E}(e_x)] = [e]$.
                              This means that $e$ has a pre-image in $E_{X}$, but because $v$ also has a pre-image in $V_{X}$ and its set of predecessors is not empty it would mean that $e$ has a predecessor which it does not.
                        \item $v$ has a pre-image $f_{V};i_{1,V}(z)$ in $V_{Z}$ such that $[f_{V}(z)) = \varnothing$ and $[g_{V}(z)) \not = \varnothing$.
                              Then, $<_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}([v])) = [i_{2,E}(e_y)] = [e]$.
                              It means that $e$ has a pre-image in $E_{Y}$, but $v$ is its source or target and has a pre-image in $V_{Y}$ which is not possible.
                        \item The remaining two cases for $v = g_{V};i_{2,V}(z)$ are symmetric.
              \end{itemize}$[<_{c,X+Y}^{\mu}(e)]$ and $e = <_{c,X+Y}^{\mu}(e)$ because edges are not identified.
                We do not need to check this requirement for nodes because a node can not be a predecessor.
        \item Let $e_1,e_2$ be edges. 
              Then, if $[e_1] = <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{E_{X} + E_{Y}}{\sim}}([e_2]))$ it must not be the case that $[e_2] = <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{E_{X} + E_{Y}}{\sim}}([e_1]))$.
              For $[e_1] = <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{E_{X} + E_{Y}}{\sim}}([e_2]))$ we have two cases.
                \item If $<_{c,X+Y}^{\mu}(i_{E_{X} + E_{Y}}(e_2)) = e_3$ then $[e_1] = [e_3]$ which yields $e_1 = e_3$.
                      Having at the same time $[e_2] = <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{E_{X} + E_{Y}}{\sim}}([e_1]))$ gives us also two cases.
                    \item $<_{c,X+Y}^{\mu}(i_{E_{X} + E_{Y}}(e_1)) = e_4$ then $[e_2] = [e_4]$ and $e_2 = e_4$.
                     This would mean that $e_1$ is a predecessor of $e_2$ and vice versa which violates the e-hypergraphness of $X+Y$.
                    \item $[e_1) = \varnothing$ and for all $v_i \in s(e_1)$ and $v_j \in t(e_1)$ $[[v_i]) \not = \varnothing$ and $[[v_j]) \not = \varnothing$.
                          Then, $[e_2] = [<_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}([v])]$.
                            \item If $v$ has no pre-image in $V_{Z}$, then 
                                [<_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}([v])] = [<_{c,X+Y}^{\mu}(i_{V_{X} + V_{Y}}(v))] = [e_2]
                                  It would mean that $e_2$ is a predecessor of $v$ and, by connectivity, a predecessor of $e_1$.
                                  However, $[e_1) = \varnothing$ and we get a contradiction.
                            \item If $v$ has a pre-image $f_{V};i_{1,V}(z)$ in $V_{Z}$ then necessarily $[f_{V}(z)) = \varnothing$ (because $[e_1) = \varnothing$) and hence $[g_{V}(z)) \not = \varnothing$.
                                    [<_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}([v])] = [i_{2,E}(e_y)] = [e_2]
                                  This means that $e_2$ has a pre-image in $E_{Y}$, but because $e_1$ is a predecessor of $e_2$ they both should have pre-image in either $E_{X}$ or $E_{Y}$.
                            \item Case when $v$ has a pre-image $g_{V};i_{2,V}(z)$ is symmetric to the above.
                    \item $[e_2) = \varnothing$ and for all $v_i \in s(e_2)$ and $v_j \in t(e_2)$ $[[v_i]) \not = \varnothing$ $[[v_j]) \not = \varnothing$.
                            <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{E_{X}+E_{Y}}{\sim}}([e_2])) = <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}([v])) = [e_1]
                          The cases when $[e_1) \not = \varnothing$ are similar to the above, so we will just jump to the interesting case when 
                          $[e_1) = \varnothing$ and
                            <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{E_{X}+E_{Y}}{\sim}}([e_1])) = <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}([v'])) = [e_2]
                          The cases we have are the following.
                            \item $v$ has no pre-image in $V_{Z}$. 
                                  Then $<_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}([v])) = [<_{c,X+Y}^{\mu}(i_{V_{X} + V_{Y}}(v))] = [e_1]$
                                  This implies that $e_1$ is the predecessor of $e_2$ because it is the predecessor of $v$ and $v$ is $e_2$'s sources of targets.
                                    \item $v'$ has no pre-image in $V_{Z}$.
                                    Then $<_{c,\sfrac{X+Y}{\sim}}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}([v'])) = [<_{c,X+Y}^{\mu}(i_{V_{X} + V_{Y}}(v'))] = [e_2]$.
                                    This implies that $e_2$ is the predecessor of $v'$ and hence of $e_1$. 
                                    This contradicts the assymetry of $<_{c,X+Y}^{\mu}$.
                                    \item $v'$ has a pre-image $f_{V};i_{1,E}(z) = v'$ in $V_{Z}$ (and so should $e_1$ do) and therefore $[f_{V}(z)) = \varnothing$ and $[g_{V}(z)) \not = \varnothing$ because $[e_1) = \varnothing$.
                                          Then, $<_{c,\sfrac{X+Y}{\sim}}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}([v'])) = [i_{2,E}(e_y)] = [e_2]$.
                                          This means that $e_2$ has a pre-image in $E_{Y}$ but $e_1$ is the predecessor of $e_2$ and hence they should both have pre-image in $E_{X}$ (as $e_1$ does so).
                                    \item Case when $v' = g_{V};i_{2,V}(z)$ is symmetric.
                            \item $v$ has a pre-image $f_{V};i_{1,V}(z)$ (and so should $e_2$ do) in $Z_{V}$ and therefore $[f_{V}(z)) = \varnothing$ and $[g_{V}(z)) \not = \varnothing$.
                                  Then, $<_{c,\sfrac{X+Y}{\sim}}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}([v])) = [g_{V};i_{V_{Y}};<_{c,Y}^{\mu};i_{2,E}(z)] = [i_{2,E}(e_{y})] = [e_1]$.
                                  This implies that $e_1$ has a pre-image in $E_{Y}$.
                                    \item $v'$ has no pre-image in $V_{Z}$.
                                          Then $<_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}([v'])) = [<_{c,X+Y}^{\mu}(i_{V_{X} + V_{Y}}(v'))] = [e_2]$.
                                          This implies that $e_2$ is the predecessor of $v'$ and hence of $e_1$.
                                          But $[e_1) = \varnothing$ and hence we have a contradiction.
                                    \item $v'$ has a pre-image $f_{V};i_{1,V}(z') = v'$ in $V_{Z}$ (and so should $e_1$ do) and therefore $[f_{V}(z')) = \varnothing$ and $[g_{V}(z')) \not = \varnothing$.
                                          This also means that $[g_{V}(z)) = [g_{V}(z'))$.
                                          By definition we have that $e_1$ is the image of the predecessor of $g_{V}(z')$ and $e_2$ is the image of the predecessor of $g_{V}(z)$ and because their predecessors are equal it implies $e_1 = e_2$ but the relation is irreflexive.
                                    \item $v'$ has a pre-image $g_{V};i_{2,V}(z') = v'$ in $V_{Z}$ and therefore $[f_{V}(z')) \not = \varnothing$ and $[g_{V}(z')) = \varnothing$.
                                          This is impossible as it violates the requirement that $[f_{V}(z)) = [f_{V}(z'))$ for all $z,z' \in V_{Z}$.
                            \item The case when $v$ has a pre-image $g_{V};i_{2,V}(z)$ is symmetric.
              Once again, we do not need to check for nodes as a node can not be on the lefthand side of the relation.
        \item We need to show that if $[v] \in s([e_1])$ and $[e_2] = <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{E_{X} + E_{Y}}{\sim}}([e_1]))$ then $[e_2] = <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}[v])$.
              $[e_2] = <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{E_{X} + E_{Y}}{\sim}}([e_1]))$ gives us two cases.
                \item If $<_{c,X+Y}^{\mu}(i_{E_{X} + E_{Y}}(e_1)) = e_3$, then $<_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{E_{X} + E_{Y}}{\sim}}([e_1])) = [<_{c,X+Y}^{\mu}(i_{E_{X} + E_{Y}}(e_1))] = [e_3] = [e_2]$ which means that $e_2$ is the predecessor of $e_1$.
                      $[v] \in s([e_1])$ means that there exists $v'$ such that $[v] = [v']$ and $v' \in s(e_1)$.
                        \item $v = v'$ then $v \in s(e_1)$ and because $e_2$ is the predecessor of $e_1$ it is also a predecessor of $v$ because $X+Y$ is an e-hypergraph.
                            That is, $e_2 = <_{c,X+Y}^{\mu}(i_{V_{X} + V_{Y}}(v))$ and we have $[e_2] = [<_{c,X+Y}^{\mu}(i_{V_{X} + V_{Y}}(v))] = <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}([v]))$.
                        \item $v \sim v'$ which means there exists $z \in V_{Z}$ such that $v = f_{V};i_{1,V}(z)$ and $v' = g_{V};i_{2,V}(z)$ and $v' \in s(e_1)$.
                              Once again, $e_2 = <_{c,X+Y}^{\mu}(i_{E_{X} + E_{Y}}(e_1))$ implies $e_2 = <_{c,X+Y}^{\mu}(i_{V_{X} + V_{Y}}(v'))$ and 
                                [e_2] = [<_{c,X+Y}^{\mu}(i_{V_{X} + V_{Y}}(v'))] = <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}([v'])) = <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}([v]))
                \item $[e_1) = \varnothing$ and for all $v_i \in s(e_1), v_j \in t(e_1)$ $[[v_i]) \not = \varnothing,\; [[v_j]) \not = \varnothing$. 
                Then, $<_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{E_{X} + E_{Y}}{\sim}}([e_1])) = <_{c,\sfrac{X+Y}{\sim}}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}([v])) = [e_2]$ and this gives us the needed property on the nose.
        \item Finally, we need to check that if $[v] \in s([e_1])$ and $[e_2] = <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}([v]))$ then $[e_2] = <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{E_{X} + E_{Y}}{\sim}}([e_1]))$.
        Once again, $[v] \in s([e_1])$ means that there exists $v' \in s(e_1)$ such that $[v'] = [v]$.
            \item $v' = v$ and hence $v \in s(e_1)$.
                \item If $v$ has no pre-image in $V_{Z}$, then $[e_2] = <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}([v])) = [<_{c,X+Y}^{\mu}(i_{V_{X} + V_{Y}}(v))]$.
                      This essentially means that $e_2$ is the predecessor of $v$ and, by e-hypergraphness of $X+Y$, $e_2 = <_{c,X+Y}^{\mu}(i_{E_{X} + E_{Y}}(e_1))$ and $[e_2] = [<_{c,X+Y}^{\mu}(i_{E_{X} + E_{Y}}(e_1))] = <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{E_{X} + E_{Y}}{\sim}}([e_1]))$ which is what we want.
                \item $v$ has a pre-image $f_{V};i_{1,V}(z)$ and $[f_{V}(z)) \not = \varnothing$ and $[g_{V}(z)) = \varnothing$, then
                    [e_2] = <_{c,\sfrac{X+Y}{\sim}}^{\mu}(i_{\sfrac{V_{X} + V_{Y}}{\sim}}([v])) = [i_{1,E}(e_x)]
                Because $e_{x}$ is the predecessor of $f_{V}(z)$ it should also be the predecessor of the pre-image of $e_1$ in $E_{X}$ as $v \in s(e_1)$.
                Denote the pre-image of $e_1$ in $E_{X}$ as $e_{1}^{x}$. 
                Then, $e_{x} = <_{c,X}^{\mu}(i_{E_{X}}(e_{1}^{x}))$ and
